### 2014-09-02 constraints.tex
more changes to tech part
edits

Given pair $\tau$ and $\tau'$ of events that both access a common memory location $\ell$, we demand that
$$
\begin{array}{rl}
					& {\sf thread}\ \tau \neq {\sf thread}\ \tau' \\
\bigwedge 	& ({\sf writes}\ \tau\ \ell \vee \tau'\ {\tt s}'\ \ell) \\
\bigwedge   & O_{\tau} = O_{\tau'}
\end{array}
$$
That is, (i) events $\tau$ and $\tau'$ are executed by different threads, (ii) at least one of the events performs write access to $\ell$, and (iii) the events occur at the simultanesouly. This is a direct logical encoding of the definition of a race condition.

@@

Beyond relaxing flow dependencies, \tool\ is also capable of exploring code branches that were not executed in the original trace. This is achieved via a symbolic representation of the input trace. Given branching event $e_b$,
\begin{enumerate}
	\item model the branching condition symbolically to execute along the negation of the original branch;
	\item apply depth-first search (DFS) to uncover all execution suffixes under the unexplored branch (which may itself contain branching statements); and
	\item for each suffix $t^s$,
	\begin{enumerate}
		\item truncate the original trace at $e_b$ {\tt s} yielding $t_s$; and
		\item concatenate $t_s$ with the negation of $e_b$ followed by $t^s$.
	\end{enumerate}
\end{enumerate}
Constraint solving is applied to each of the resulting traces analogously to the original trace.

@@

>>>>

Given pair $\tau$ and $\tau'$ of events that both access a common memory location $\ell$, we demand that
$$
\begin{array}{rl}
					& {\sf thread}\ \tau \neq {\sf thread}\ \tau' \\
\bigwedge 	& (\ell \in {\sf writeset}\ \tau \vee \ell \in {\sf writeset}\ \tau') \\
\bigwedge   & O_{\tau} = O_{\tau'}
\end{array}
$$
That is, (i) events $\tau$ and $\tau'$ are executed by different threads, (ii) at least one of the events performs write access to $\ell$ (as judged by the ${\sf writeset}$ membership check), and (iii) the events occur simultanesouly. This is a direct logical encoding of the definition of a race condition.

@@

Beyond relaxing flow dependencies, \tool\ is also capable of exploring code branches that were not executed in the original trace. This is achieved via a symbolic representation of the input trace. Given branching event $e_b$,
\begin{enumerate}
	\item model the branching condition symbolically to execute along the negation of the original branch;
	\item apply depth-first search (DFS) to uncover all execution suffixes under the unexplored branch (which may itself contain branching statements); and
	\item for each suffix $t^s$,
	\begin{enumerate}
		\item truncate the original trace at $e_b$ yielding prefix $t_s$; and
		\item concatenate $t_s$ with the negation of $e_b$ followed by $t^s$.
	\end{enumerate}
\end{enumerate}
Constraint solving is applied to each of the resulting traces analogously to the original trace.

@@

\subsection{Proof of Correctness}

\input{proof}
